---
title: "fMRI_chronoTMS_Blind_Sighted_PLOTS"
author: "Jacek Matuszewski"
date: '2022-08-16'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      results = 'hide')
```

```{r load packages, echo=, message=FALSE, warning=FALSE}
#library(plotly)
library(tidyverse)
library(ggsignif)
library(cowplot)
library(RColorBrewer)
library(patchwork)
library(ggpubr)
```

---------- MAIN PLOTTING FUNCTIONS --------- 
```{r}
dir <- "/Users/jacekmatuszewski/Documents/GitHub/fMRI_chronoTMS_Blind_Sighted"

source(paste(dir, 'code', 'functions_plots.R', sep = '/'))

```


# --------------- BEHAVIOURAL PLOTS ---------------

Load the data and prepare the dataframes

```{r}

#Read the data
mri_behav <- read.csv(paste(dir, 'data', 'fMRI', 'MRI_behav.csv', sep ='/'))

#Prepare the data frame for reading speed
df.beh.reading <- mri_behav %>% 
    dplyr::select(subject, group = Group, speed_words, speed_pseudo) %>% 
    pivot_longer(cols = speed_words:speed_pseudo, 
                 names_to = "lexicality", 
                 values_to = "speed") %>% 
    mutate(lexicality = sub("speed_", "", lexicality, ignore.case = TRUE)) %>%
    mutate(lexicality = gsub("pseudo", "pseudowords", lexicality)) %>% 
    mutate(lexicality = sub("(.)", "\\U\\1", lexicality, perl=TRUE))

#Prepare the data frame for 1-back task
df.beh.task <- mri_behav %>% 
    dplyr::select(-speed_words, -speed_pseudo, 
           group = Group, 
           Speech_Words = d_prime_speech_words,
           Speech_Pseudowords = d_prime_speech_pseudowords,
           Speech_Control = d_prime_speech_ctrl,
           Reading_Words = d_prime_read_words,
           Reading_Pseudowords = d_prime_read_pseudowords,
           Reading_Control = d_prime_read_ctrl) %>% 
    pivot_longer(cols = Speech_Words:Reading_Control, 
                 names_sep = "_",
                 names_to = c("modality", "condition"),
                 values_to = "d_prime")

#smol clean up
rm(mri_behav)
```

PLOT BEH: READING SPEED

```{r}
#PLOT WITH FUNCTION
plot.beh.reading.speed <- beh_reading_speed_points(data = df.beh.reading)
```

PLOT BEH: fMRI 1-back task

```{r}
## POINTS WITH MEAN
plot.beh.fmri.task.rd <- beh_task_points(df.beh.task, mod = "Reading")
plot.beh.fmri.task.sp <- beh_task_points(df.beh.task, mod = "Speech")

#COMBINE & CLEAN
plot.beh.fmri.task.grid <- plot.beh.fmri.task.rd + plot.beh.fmri.task.sp

rm(plot.beh.fmri.task.rd, plot.beh.fmri.task.sp)
```



# --------------- fMRI ROI PLOTS ---------------

Load the data
```{r}
#Load the data

load(paste(dir, 'data', 'fMRI', 'ROI_data.RData', sep = '/'))
    
#Prepare a longer version of the DF to be filtered in functions
df.fmri.roi <- rois_long %>% 
    dplyr::select(-c(V1_bilateral, visf_pOTS, visf_IOS)) %>% 
    pivot_longer(names_to = "ROI", 
                 values_to = "Contrast_Estimate",
                 cols = c("visf_v1", "VWFA_cohen_5")) %>% 
    mutate(ROI = recode(ROI, "visf_v1" = "V1",
                  "VWFA_cohen_5" = "VWFA"))

rm(rois_long)
```

Plot the data

```{r}
#PLOT JITTER + MEANS & SEMS (BLACK!)
plot.fMRI.v1.bl <- fMRI_ROI_points(data = df.fmri.roi, 
                                 roi = "V1", 
                                 sub_group = "Blind") + theme(legend.position = "none")

plot.fMRI.v1.si <- fMRI_ROI_points(data = df.fmri.roi,
                                   roi = "V1", 
                                   sub_group = "Sighted") + theme(legend.position = "none")


plot.fMRI.vwfa.bl <- fMRI_ROI_points(data = df.fmri.roi, 
                                 roi = "VWFA", 
                                 sub_group = "Blind") + theme(legend.position = "bottom")

plot.fMRI.vwfa.si  <- fMRI_ROI_points(data = df.fmri.roi,
                                   roi = "VWFA", 
                                   sub_group = "Sighted") + theme(legend.position = "bottom")


#COMBINE INTO A 2-by-2 GRID AND CLEAN UP PARTIAL PLOTS
#plot.fMRI.grid <- plot.fMRI.v1.bl / plot.fMRI.vwfa.bl  | plot.fMRI.v1.si / plot.fMRI.vwfa.si

#ADDED BIT OF VERTICAL SPACE BETWEEN PANELS FOR STAT SIGNIFICANCE
plot.fMRI.grid <- plot.fMRI.v1.bl / plot_spacer() / plot.fMRI.vwfa.bl + plot_layout(heights = c(4,1,4)) | plot.fMRI.v1.si / plot_spacer() /plot.fMRI.vwfa.si + plot_layout(heights = c(4,1,4))

rm(plot.fMRI.v1.bl, plot.fMRI.vwfa.bl, plot.fMRI.v1.si, plot.fMRI.vwfa.si)
```


# --------------- TMS PLOTS: GLM DATA ---------------
## GLM MAIN PLOTS OVER TIME
GLM DATA: load the DFs
```{r}
##Loads DFs for main plots, lexicality across sites and main effects of lexicality
#RT
load(paste(dir, 'data', 'TMS', 'GLM_RT_plot_data.RData', sep = '/'))
#ACCU
load(paste(dir, 'data', 'TMS', 'GLM_ACCU_plot_data.RData', sep = '/'))
```


PLOTS GLM RT: GROUP x SITE x MODALITY x TIME
```{r}
# BLIND: RT EMMEANS
#Reading
plot.tms.rt.glm.bl.rd <- tms_line_mod_sep_glm(data = df.rt.glm.tms.effects, 
                                                   sub_group = "Blind", 
                                                   metric = "RT", 
                                                   mod = "read")
#Speach
plot.tms.rt.glm.bl.sp <- tms_line_mod_sep_glm(data = df.rt.glm.tms.effects, 
                                                   sub_group = "Blind", 
                                                   metric = "RT", 
                                                   mod = "speech")

# SIGHTED: RT EMMEANS
#Reading
plot.tms.rt.glm.si.rd <- tms_line_mod_sep_glm(data = df.rt.glm.tms.effects, 
                                                   sub_group = "Sighted", 
                                                   metric = "RT", 
                                                   mod = "read")

#Speech
plot.tms.rt.glm.si.sp <- tms_line_mod_sep_glm(data = df.rt.glm.tms.effects, 
                                                   sub_group = "Sighted", 
                                                   metric = "RT", 
                                                   mod = "speech")

#COMBINE INTO A 2-by-2 GRID AND CLEAN UP PARTIAL PLOTS
plot.tms.rt.glm.grid <- plot.tms.rt.glm.bl.rd / plot.tms.rt.glm.bl.sp | plot.tms.rt.glm.si.rd / plot.tms.rt.glm.si.sp
rm(plot.tms.rt.glm.bl.rd, plot.tms.rt.glm.bl.sp, plot.tms.rt.glm.si.rd, plot.tms.rt.glm.si.sp)
```

PLOTS GLM ACCU: GROUP x SITE x MODALITY x TIME
```{r}
#BLIND: ACCURACY EMMEANS (LOGIT SCALE)
#Reading
plot.tms.accu.glm.bl.rd <- tms_line_mod_sep_glm(data = df.accu.glm.tms.effects, 
                                                   sub_group = "Blind", 
                                                   metric = "Accuracy", 
                                                   mod = "read")
#Speech
plot.tms.accu.glm.bl.sp <- tms_line_mod_sep_glm(data = df.accu.glm.tms.effects, 
                                                   sub_group = "Blind", 
                                                   metric = "Accuracy", 
                                                   mod = "speech")

#SIGHTED: ACCURACY EMMEANS (LOGIT SCALE)
#Reading
plot.tms.accu.glm.si.rd <- tms_line_mod_sep_glm(data = df.accu.glm.tms.effects, 
                                                   sub_group = "Sighted", 
                                                   metric = "Accuracy", 
                                                   mod = "read")
#Speech
plot.tms.accu.glm.si.sp <- tms_line_mod_sep_glm(data = df.accu.glm.tms.effects, 
                                                   sub_group = "Sighted", 
                                                   metric = "Accuracy", 
                                                   mod = "speech")

#COMBINE INTO A 2-by-2 GRID AND CLEAN UP PARTIAL PLOTS
plot.tms.accu.glm.grid <- plot.tms.accu.glm.bl.rd / plot.tms.accu.glm.bl.sp | plot.tms.accu.glm.si.rd / plot.tms.accu.glm.si.sp
rm(plot.tms.accu.glm.bl.rd, plot.tms.accu.glm.bl.sp, plot.tms.accu.glm.si.rd, plot.tms.accu.glm.si.sp)
```



## GLM LEXICALITY: PLOTS OVER TIME

RT GLM: Lexicality over time
```{r}
## PLOT  RT ACROSS LEXICALITES


# THIS PART HAS BEEN UPDATED IN A PLOTTING FUNCTION
#prep the df to work with plotting function
df.rt.glm.lex_time_tms_effects <- df.rt.glm.lex_time_tms_effects %>%
   # rename(mean = estimate) %>%
   # rename(sem = SE) %>%
    rename(TW = contrast)

#Blind: Reading
plot.tms.rt.glm.lex.time.bl.rd <- tms_line_mod_sep_glm_lex(df.rt.glm.lex_time_tms_effects, 
                                                       sub_group = "Blind",
                                                       mod = "read", 
                                                       metric = "RT")  
#Blind: Speech
plot.tms.rt.glm.lex.time.bl.sp <- tms_line_mod_sep_glm_lex(df.rt.glm.lex_time_tms_effects, 
                                                       sub_group = "Blind",
                                                       mod = "speech", 
                                                       metric = "RT")
#Sighted: Reading
plot.tms.rt.glm.lex.time.si.rd <- (tms_line_mod_sep_glm_lex(df.rt.glm.lex_time_tms_effects,
                                                       sub_group = "Sighted",
                                                       mod = "read", 
                                                       metric = "RT")+theme(legend.position = "none"))
#Sighted: Speech
plot.tms.rt.glm.lex.time.si.sp <- tms_line_mod_sep_glm_lex(df.rt.glm.lex_time_tms_effects,
                                                       sub_group = "Sighted",
                                                       mod = "speech", 
                                                       metric = "RT")

#COMBINE INTO A 2-by-2 GRID AND CLEAN UP PARTIAL PLOTS
plot.tms.rt.glm.lex.time.grid <- plot.tms.rt.glm.lex.time.bl.rd / plot.tms.rt.glm.lex.time.bl.sp | plot.tms.rt.glm.lex.time.si.rd / plot.tms.rt.glm.lex.time.si.sp

rm(plot.tms.rt.glm.lex.time.bl.rd, plot.tms.rt.glm.lex.time.bl.sp, plot.tms.rt.glm.lex.time.si.rd, plot.tms.rt.glm.lex.time.si.sp)
```

ACCU GLM: Lexicality over time
```{r}
## PLOT LOGIT ACCURACY ACROSS LEXICALITES
#Blind: Reading
plot.tms.accu.glm.lex.time.bl.rd <- tms_line_mod_sep_glm_lex(df.accu.glm.lex_time_tms_effects, 
                                                       sub_group = "Blind",
                                                       mod = "read", 
                                                       metric = "Accuracy") 
#Blind: Speech
plot.tms.accu.glm.lex.time.bl.sp <- tms_line_mod_sep_glm_lex(df.accu.glm.lex_time_tms_effects, 
                                                       sub_group = "Blind",
                                                       mod = "speech", 
                                                       metric = "Accuracy")
#Sighted: Reading
plot.tms.accu.glm.lex.time.si.rd <- tms_line_mod_sep_glm_lex(df.accu.glm.lex_time_tms_effects,
                                                       sub_group = "Sighted",
                                                       mod = "read", 
                                                       metric = "Accuracy")  
#Sighted: Speech
plot.tms.accu.glm.lex.time.si.sp <- tms_line_mod_sep_glm_lex(df.accu.glm.lex_time_tms_effects,
                                                       sub_group = "Sighted",
                                                       mod = "speech", 
                                                       metric = "Accuracy")


#COMBINE INTO A 2-by-2 GRID AND CLEAN UP PARTIAL PLOTS
plot.tms.accu.glm.lex.time.grid <- plot.tms.accu.glm.lex.time.bl.rd / plot.tms.accu.glm.lex.time.bl.sp | plot.tms.accu.glm.lex.time.si.rd / plot.tms.accu.glm.lex.time.si.sp
rm(plot.tms.accu.glm.lex.time.bl.rd, plot.tms.accu.glm.lex.time.bl.sp, plot.tms.accu.glm.lex.time.si.rd, plot.tms.accu.glm.lex.time.si.sp)
```




## GLM LEXICALITY: MAIN EFFECT OF LEX
RT GLM: Lex ME
```{r}
# PLOT EMMEANS for words and pseudowords (across modalities and groups )
#Blind: reading
plot.tms.rt.glm.lex.me.bl.rd <- tms_main_effects_lex(data = df.rt.glm.lex_me, 
                                          sub_group = "Blind", 
                                          mod = "read")
#Blind: speech
plot.tms.rt.glm.lex.me.bl.sp <- tms_main_effects_lex(data = df.rt.glm.lex_me, 
                                          sub_group = "Blind", 
                                          mod = "speech")

#Sighted: reading
plot.tms.rt.glm.lex.me.si.rd<- tms_main_effects_lex(data = df.rt.glm.lex_me, 
                                          sub_group = "Sighted", 
                                          mod = "read")
#Sighted: speech
plot.tms.rt.glm.lex.me.si.sp <- tms_main_effects_lex(data = df.rt.glm.lex_me, 
                                          sub_group = "Sighted", 
                                          mod = "speech")


#COMBINE INTO A 2-by-2 GRID AND CLEAN UP PARTIAL PLOTS
plot.tms.rt.glm.lex.me.grid <- plot.tms.rt.glm.lex.me.bl.rd / plot.tms.rt.glm.lex.me.bl.sp | plot.tms.rt.glm.lex.me.si.rd / plot.tms.rt.glm.lex.me.si.sp
rm(plot.tms.rt.glm.lex.me.bl.rd, plot.tms.rt.glm.lex.me.bl.sp, plot.tms.rt.glm.lex.me.si.rd, plot.tms.rt.glm.lex.me.si.sp)

```

ACCU GLM: Lex ME
```{r}
# PLOT EMMEANS for words and pseudowords (main effects)
# Accuracy plots require tweaking due to scale differences

#Blind: reading
plot.tms.accu.glm.lex.me.bl.rd <- tms_main_effects_lex(data = df.accu.glm.lex_me, 
                                          sub_group = "Blind", 
                                          mod = "read") + 
    ylab("Accuracy [logit]") +
    scale_y_continuous(limits = c(2.4, 4.1))

#Blind: speech
plot.tms.accu.glm.lex.me.bl.sp <- tms_main_effects_lex(data = df.accu.glm.lex_me, 
                                          sub_group = "Blind", 
                                          mod = "speech") + 
    ylab("Accuracy [logit]") +
    scale_y_continuous(limits = c(2.4, 4.1))

#Sighted: reading
plot.tms.accu.glm.lex.me.si.rd <- tms_main_effects_lex(data = df.accu.glm.lex_me, 
                                          sub_group = "Sighted", 
                                          mod = "read") + 
    ylab("Accuracy [logit]") +
    scale_y_continuous(limits = c(2.4, 4.1))

#Sighted: speech
plot.tms.accu.glm.lex.me.si.sp <- tms_main_effects_lex(data = df.accu.glm.lex_me, 
                                          sub_group = "Sighted", 
                                          mod = "speech") + 
    ylab("Accuracy [logit]") +
    scale_y_continuous(limits = c(2.4, 4.1))

#COMBINE INTO A 2-by-2 GRID AND CLEAN UP PARTIAL PLOTS
plot.tms.accu.glm.lex.me.grid <- plot.tms.accu.glm.lex.me.bl.rd / plot.tms.accu.glm.lex.me.bl.sp | plot.tms.accu.glm.lex.me.si.rd / plot.tms.accu.glm.lex.me.si.sp
rm(plot.tms.accu.glm.lex.me.bl.rd, plot.tms.accu.glm.lex.me.bl.sp, plot.tms.accu.glm.lex.me.si.rd, plot.tms.accu.glm.lex.me.si.sp)
```







# --------------- TMS PLOTS: RAW DATA --------------- 
## DF PREPARATION & CLEAN-UP

Load and wrangle the DFs for raw data
```{r}
load(paste(dir, 'data', 'TMS', 'TMS_preprocessed_data.RData', sep = '/'))

## ---------- Raw data, bound across groups (all trials) ----------
raw_data_all <- rbind(blind_raw_data, sighted_raw_data) %>% 
     filter(Subject != "Sighted_11") %>% 
     mutate(Accuracy_01 = recode (Accuracy, 
                              "hit" = 1, 
                              "incorrect" = 0,
                              "miss" = 0))


```

RAW RT MAIN DF 
```{r}
## ---------- RAW RTs: MEANS ---------- 

rt_data_all <- rbind(blind_rt_data, sighted_rt_data) %>% 
        filter(Subject != "Sighted_11")

## TMS effects for each subject!  
rt_tms_effects <- rt_data_all %>% 
     group_by(Subject, Site, Modality) %>% 
     #compute TMS effects for each subject * condition
     mutate(RT_mean_TMS_effect = RT_mean-RT_mean[TW=="ctrlTMS"]) %>%
     filter(TW != "ctrlTMS") %>%
     dplyr::select(Subject, Group, Site, Modality, TW, RT_mean_TMS_effect)
    
df.rt.raw.tms.effects <- rt_tms_effects %>% 
     group_by(Group, Site, Modality, TW) %>% 
     dplyr::summarize(mean = mean(RT_mean_TMS_effect), 
                      sem = sd(RT_mean_TMS_effect)/sqrt(25))


```


RAW RT LEX DF
```{r}
## ---------- RAW RTs: LEXICALITY MEANS --------- 
#Prepare the DATA FRAMES
rt_data_lex <- raw_data_all %>% 
    filter(Accuracy == "hit") %>% 
    mutate(Lex = factor(Lex, levels = c("word", "pseudo"))) %>% 
    group_by(Subject, Group, Site, Modality, TW, Lex) %>% 
    summarise(RT_mean = mean(RT))

## TMS effects for each subject!  
rt_tms_effects_lex <- rt_data_lex %>% 
     group_by(Subject, Site, Modality, Lex) %>% 
     #compute TMS effects for each subject * condition
     mutate(RT_mean_TMS_effect = RT_mean-RT_mean[TW=="ctrlTMS"]) %>%
     filter(TW != "ctrlTMS") %>%
     dplyr::select(Subject, Group, Site, Modality, TW, Lex, 
                   RT_mean_TMS_effect)

 #Summaries for median RTs
df.rt.raw.lex_time_tms_effects <- rt_tms_effects_lex %>% 
     group_by(Group, Site, Modality, TW, Lex) %>% 
     dplyr::summarize(mean = mean(RT_mean_TMS_effect), 
                      sem = sd(RT_mean_TMS_effect)/sqrt(25))

```


RAW ACCU MAIN DF
```{r}
## ---------- "RAW" ACCURACIES ---------- 

# For "raw" plots and interpretable values (vs log odds ratio)
accu_data_all <- rbind(blind_accuracy_data, sighted_accuracy_data) %>%
    filter(Subject != "Sighted_11") %>%
    mutate(Error_rate = 1 - Accuracy_score)


accu_tms_effects <- accu_data_all %>%
      mutate(Error_rate = (1 - Accuracy_score) * 100) %>%
      group_by(Subject, Site, Modality) %>%
      #compute TMS effects for each subject * condition
      mutate(Accuracy_TMS_effect = Accuracy_score-Accuracy_score[TW == "ctrlTMS"]) %>%
      #mutate(Error_rate_TMS_effect = Error_rate-Error_rate[TW == "ctrlTMS"]) %>%
      filter(TW != "ctrlTMS")

# Create summaries with % (* 100)
df.accu.raw.tms.effects <- accu_tms_effects %>%
    group_by(Group, Site, Modality, TW) %>%
    dplyr::summarise(mean = mean(Accuracy_TMS_effect) * 100,
                     sem = (sd(Accuracy_TMS_effect)/sqrt(25)) * 100)

rm(accu_tms_effects, accu_data_all)
```

RAW ACCU LEX DF
```{r}
## --------- "RAW" ACCURACIES: LEXICALITY EFFECTS --------- 

accu_data_lex <- raw_data_all %>%
    filter(Subject != "Sighted_11") %>% 
    mutate(Lex = factor(Lex, levels = c("word", "pseudo"))) %>% 
    group_by(Subject, Group, Site, Modality, TW, Lex) %>% 
    summarise(Accuracy_score = sum(Accuracy_01)/10)
              
## TMS effects for each subject!  
 accu_tms_effects_lex <- accu_data_lex %>% 
     group_by(Subject, Site, Modality, Lex) %>% 
     #compute TMS effects for each subject * condition
     mutate(Accu_TMS_effect = Accuracy_score-Accuracy_score[TW=="ctrlTMS"]) %>%
     filter(TW != "ctrlTMS") %>%
     dplyr::select(Subject, Group, Site, Modality, TW, Lex, Accu_TMS_effect)

 
#Summaries for ACCURACY RATES
df.accu.raw.lex_time_tms_effects <- accu_tms_effects_lex %>% 
     group_by(Group, Site, Modality, TW, Lex) %>% 
     dplyr::summarize(mean = mean(Accu_TMS_effect) * 100, 
                      sem = sd(Accu_TMS_effect)/sqrt(25) * 100)
 
 rm(accu_data_lex, accu_tms_effects_lex)
```

CLEAN UP
```{r}
#smol clean-up
rm(blind_accuracy_data, sighted_accuracy_data,
   blind_rt_data, sighted_rt_data,
   blind_raw_data, sighted_raw_data, 
   tms_preproc, blind_percent_trimmed, 
   sighted_percent_trimmed, raw_data_all, 
   rt_data_all, rt_data_lex, rt_tms_effects,
   rt_tms_effects_lex)
```


RT: mean + SE (TMS effects)
```{r}
## COMPARE THAT TO RAW PLOTS (MEAN + SE)
plot.tms.rt.raw.bl.rd <- tms_line_mod_sep_raw(data = df.rt.raw.tms.effects, 
                                        sub_group = "Blind",
                                        metric = "RT",
                                        mod = "read")  

plot.tms.rt.raw.bl.sp <- tms_line_mod_sep_raw(data = df.rt.raw.tms.effects, 
                                        sub_group = "Blind",
                                        metric = "RT",
                                        mod = "speech")

plot.tms.rt.raw.si.rd <- tms_line_mod_sep_raw(data = df.rt.raw.tms.effects, 
                                        sub_group = "Sighted",
                                        metric = "RT", 
                                        mod = "read") 

plot.tms.rt.raw.si.sp <- tms_line_mod_sep_raw(data = df.rt.raw.tms.effects, 
                                        sub_group = "Sighted",
                                        metric = "RT",
                                        mod = "speech")
```

Accuracy: Accuracy rates (TMS effects)
```{r}
## COMPARE THAT TO RAW PLOTS (ACCURACY RATE, NOT ERRORS)
plot.tms.accu.raw.bl.rd <- tms_line_mod_sep_raw(data = df.accu.raw.tms.effects, 
                                        sub_group = "Blind",
                                        metric = "Accuracy",
                                        mod = "read") 

plot.tms.accu.raw.bl.sp <- tms_line_mod_sep_raw(data = df.accu.raw.tms.effects, 
                                        sub_group = "Blind",
                                        metric = "Accuracy",
                                        mod = "speech")

plot.tms.accu.raw.si.rd <- tms_line_mod_sep_raw(data = df.accu.raw.tms.effects, 
                                        sub_group = "Sighted",
                                        metric = "Accuracy",
                                        mod = "read") 

plot.tms.accu.raw.si.sp <- tms_line_mod_sep_raw(data = df.accu.raw.tms.effects, 
                                        sub_group = "Sighted",
                                        metric = "Accuracy",
                                        mod = "speech")
```


## RAW MAIN PLOTS OVER TIME 
RT: mean + SE (TMS effects)
```{r}
#RAW OBSERVED RT PLOTS: MEAN + SE # SEPARATE_MODALITIES ONE COLOR
#Blind: reading
plot.tms.rt.raw.bl.rd  <- tms_line_mod_sep_raw(data = df.rt.raw.tms.effects,
                                       sub_group = "Blind", 
                                       metric = "RT", 
                                       mod = "read")
#Blind: speech
plot.tms.rt.raw.bl.sp  <- tms_line_mod_sep_raw(data = df.rt.raw.tms.effects,
                                       sub_group = "Blind", 
                                       metric = "RT", 
                                       mod = "speech")
#Sighted: reading
plot.tms.rt.raw.si.rd  <- tms_line_mod_sep_raw(data = df.rt.raw.tms.effects,
                                       sub_group = "Sighted", 
                                       metric = "RT", 
                                       mod = "read")
#Sighted: speech
plot.tms.rt.raw.si.sp  <- tms_line_mod_sep_raw(data = df.rt.raw.tms.effects,
                                       sub_group = "Sighted", 
                                       metric = "RT", 
                                       mod = "speech")


#COMBINE INTO A 2-by-2 GRID AND CLEAN UP PARTIAL PLOTS
plot.tms.rt.raw.grid <- plot.tms.rt.raw.bl.rd / plot.tms.rt.raw.bl.sp | plot.tms.rt.raw.si.rd / plot.tms.rt.raw.si.sp
rm(plot.tms.rt.raw.bl.rd, plot.tms.rt.raw.bl.sp, plot.tms.rt.raw.si.rd, plot.tms.rt.raw.si.sp)

```


Accuracy: Accuracy rates (TMS effects)
```{r}
#RAW ACCURACY RATES TMS EFFECTS (% CORRECT)
#Blind: reading
plot.tms.accu.raw.bl.rd <- tms_line_mod_sep_raw(df.accu.raw.tms.effects, 
                                                       sub_group = "Blind",
                                                       mod = "read", 
                                                       metric = "Accuracy")
#Blind: speech
plot.tms.accu.raw.bl.sp <- tms_line_mod_sep_raw(df.accu.raw.tms.effects, 
                                                       sub_group = "Blind",
                                                       mod = "speech", 
                                                       metric = "Accuracy")
#Sighted reading
plot.tms.accu.raw.si.rd<- tms_line_mod_sep_raw(df.accu.raw.tms.effects,
                                                       sub_group = "Sighted",
                                                       mod = "read", 
                                                       metric = "Accuracy")
#Sighted:speech
plot.tms.accu.raw.si.sp <- tms_line_mod_sep_raw(df.accu.raw.tms.effects,
                                                       sub_group = "Sighted",
                                                       mod = "speech", 
                                                       metric = "Accuracy")

#COMBINE INTO A 2-by-2 GRID AND CLEAN UP PARTIAL PLOTS
plot.tms.accu.raw.grid <- plot.tms.accu.raw.bl.rd / plot.tms.accu.raw.bl.sp | plot.tms.accu.raw.si.rd / plot.tms.accu.raw.si.sp
rm(plot.tms.accu.raw.bl.rd, plot.tms.accu.raw.bl.sp, plot.tms.accu.raw.si.rd, plot.tms.accu.raw.si.sp)
```


## RAW LEXICALITY: PLOTS OVER TIME
RT: mean + SE x LEX (TMS effects)
```{r}
#Blind: reading
plot.tms.rt.raw.lex.time.bl.rd <- tms_line_mod_sep_raw_lex(df.rt.raw.lex_time_tms_effects, 
                                                       sub_group = "Blind",
                                                       mod = "read", 
                                                       metric = "RT")  + theme(legend.position = "none")
#Blind: speech
plot.tms.rt.raw.lex.time.bl.sp <- tms_line_mod_sep_raw_lex(df.rt.raw.lex_time_tms_effects, 
                                                       sub_group = "Blind",
                                                       mod = "speech", 
                                                       metric = "RT")
#Sighted: reading
plot.tms.rt.raw.lex.time.si.rd <- tms_line_mod_sep_raw_lex(df.rt.raw.lex_time_tms_effects,
                                                       sub_group = "Sighted",
                                                       mod = "read", 
                                                       metric = "RT")  
#Sighted: speech
plot.tms.rt.raw.lex.time.si.sp <- tms_line_mod_sep_raw_lex(df.rt.raw.lex_time_tms_effects,
                                                       sub_group = "Sighted",
                                                       mod = "speech", 
                                                       metric = "RT")


#COMBINE INTO A 2-by-2 GRID AND CLEAN UP PARTIAL PLOTS
plot.tms.rt.raw.lex.time.grid <- plot.tms.rt.raw.lex.time.bl.rd / plot.tms.rt.raw.lex.time.bl.sp | plot.tms.rt.raw.lex.time.si.rd / plot.tms.rt.raw.lex.time.si.sp
rm(plot.tms.rt.raw.lex.time.bl.rd, plot.tms.rt.raw.lex.time.bl.sp, plot.tms.rt.raw.lex.time.si.rd, plot.tms.rt.raw.lex.time.si.sp)
```

Accuracy rates x LEX (TMS effects)
```{r}
plot.tms.accu.raw.lex.time.bl.rd <- tms_line_mod_sep_raw_lex(df.accu.raw.lex_time_tms_effects, 
                                                       sub_group = "Blind",
                                                       mod = "read", 
                                                       metric = "Accuracy") 

plot.tms.accu.raw.lex.time.bl.sp <- tms_line_mod_sep_raw_lex(df.accu.raw.lex_time_tms_effects, 
                                                       sub_group = "Blind",
                                                       mod = "speech", 
                                                       metric = "Accuracy")

plot.tms.accu.raw.lex.time.si.rd <- tms_line_mod_sep_raw_lex(df.accu.raw.lex_time_tms_effects,
                                                       sub_group = "Sighted",
                                                       mod = "read", 
                                                       metric = "Accuracy") 

plot.tms.accu.raw.lex.time.si.sp <- tms_line_mod_sep_raw_lex(df.accu.raw.lex_time_tms_effects,
                                                       sub_group = "Sighted",
                                                       mod = "speech", 
                                                       metric = "Accuracy")

#COMBINE INTO A 2-by-2 GRID AND CLEAN UP PARTIAL PLOTS
plot.tms.accu.raw.lex.time.grid <- plot.tms.accu.raw.lex.time.bl.rd / plot.tms.accu.raw.lex.time.bl.sp | plot.tms.accu.raw.lex.time.si.rd / plot.tms.accu.raw.lex.time.si.sp
rm(plot.tms.accu.raw.lex.time.bl.rd, plot.tms.accu.raw.lex.time.bl.sp, plot.tms.accu.raw.lex.time.si.rd, plot.tms.accu.raw.lex.time.si.sp)
```



# ---------- SAVE ALL PLOTS ----------
Couple of scaling / dimensions options are needed for different kinds of plots
1. Beh: reading speed
2. Beh: task 
3. fMRI: ROI
4. TMS: big grids
5. TMS: me lex

## BEH & fMRI PLOTS
```{r}
fig_dir <- "/Users/jacekmatuszewski/Library/CloudStorage/OneDrive-UCL/manuscript_TMS_Blind_Sighted/draft/R_figures/"

#Overrride the ggsave function to use white bg
ggsave <- function(..., bg = 'white') ggplot2::ggsave(..., bg = bg)

## HOW TO LIST ALL GGPLOTS IN ENV
#ggplot_list <- Filter(function(x) is(x, "ggplot"), mget(ls()))

## HOW TO LIST GGPLOTS IN ENV BASED ON NAME PATTERN
#ggplot_behlist <- Filter(function(x) is(x, "ggplot"), mget(ls(pattern = "^plot.beh*")))


#READING SPEED
 ggsave(filename = paste0(fig_dir, "plot.beh.reading.speed.tiff"),
                plot = plot.beh.reading.speed,
                units = "px",
                height = 500,
                width = 600,
                dpi = 300,
                scale = 3.5)

#fMRI TASK PERFORMANCE
  ggsave(filename = paste0(fig_dir, "plot.beh.fmri.task.grid.tiff"),
                plot = plot.beh.fmri.task.grid,
                units = "px",
                height = 400,
                width = 1400,
                dpi = 300,
                scale = 3.5)

  
#fMRI ROIs DATA
    ggsave(filename = paste0(fig_dir, "plot.fmri.roi.grid.tiff"),
                plot = plot.fMRI.grid,
                units = "px",
                height = 1000,
                width = 1600,
                dpi = 300,
                scale = 3.2)
  
```

## TMS PLOTS
```{r}
#Plots DIR
fig_dir <- paste(dir, 'plots', sep = '/')
dir.create(fig_dir)

#Overrride the ggsave function to use white bg
ggsave <- function(..., bg = 'white') ggplot2::ggsave(..., bg = bg)

#List TMS grid plots
ggplot_tms_grid_list <- Filter(function(x) is(x, "ggplot"), mget(ls(pattern = "^plot.tms.*.grid")))
tms_grid_plot_list <- ls(pattern = "^plot.tms.*.grid")

#Loop across main grids
for(i in seq_along(ggplot_tms_grid_list)) {

        ggsave(filename = paste0(fig_dir, tms_grid_plot_list[i], ".tiff"),
               plot = ggplot_tms_grid_list[[i]],
               units = "px",
               height = 1000,
               width = 2000,
               dpi = 300,
               scale = 3.2)
}

#List TMS ME plots
ggplot_tms_me_list <- Filter(function(x) is(x, "ggplot"), mget(ls(pattern = "*.lex.me.grid")))
tms_me_plot_list <- ls(pattern = "*.lex.me.grid")

#Loop across me plots, overrride previous ones! 
for(i in seq_along(ggplot_tms_me_list)) {

        ggsave(filename = paste0(fig_dir, tms_me_plot_list[i], ".tiff"),
               plot = ggplot_tms_me_list[[i]],
               units = "px",
               height = 800,
               width = 1000,
               dpi = 300,
               scale = 3.2)
}
```

DONE? 
```{r}
print("DONE WITHOUT ERRORS, HAVE A COOKIE")
```

