---
title: "fMRI_chronoTMS_Blind_Sighted_TMS_Accuracy"
author: "Jacek Matuszewski"
date: '2022-08-16'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, echo=, message=FALSE, warning=FALSE}
#library(plotly)
library(tidyverse)
#library(ggsignif)
library(lme4)
library(lmerTest)
library(jtools)
library(ez)
library(tidyverse)
library(stringr)
library(cowplot)
library(RColorBrewer)
library(patchwork)
library(nlme)
library(multcomp)
library(emmeans)
```

Load the data frames and create Data Frames for linear models (RT & Accuracy)

```{r Load preprocessed data, echo=}
#Requires running TMS_MNI_and_preproc.Rmd first
rm(list=ls())

dir <- '/Users/jacekmatuszewski/Documents/GitHub/fMRI_chronoTMS_Blind_Sighted'
load(paste(dir, 'data', 'TMS', 'TMS_preprocessed_data.RData', sep = '/'))

## Prepare DFs for GLMMs: raw data withh all answers (ACCU) and correct only (RT)

## ---------- Raw data, bound across groups (all trials) ----------
raw_data_all <- rbind(blind_raw_data, sighted_raw_data) %>% 
     filter(Subject != "Sighted_11") %>% 
     mutate(Accuracy_01 = recode (Accuracy, 
                              "hit" = 1, 
                              "incorrect" = 0,
                              "miss" = 0))


#Count for descriptive purposes (hits / misses occurences)
#raw_data_all %>% count(Accuracy)

#raw_data_corr_incorr <- raw_data_all %>% filter(Accuracy != "miss")  
     
 

## ---------- ERROR RATES: "RAW" ACCURACIES ---------- 

# For "raw" plots and interpretable values (vs log odds ratio)

 
accu_data_all <- rbind(blind_accuracy_data, sighted_accuracy_data) %>%
    filter(Subject != "Sighted_11") %>%
    mutate(Error_rate = 1 - Accuracy_score)


accu_tms_effects <- accu_data_all %>%
      mutate(Error_rate = (1 - Accuracy_score) * 100) %>%
      group_by(Subject, Site, Modality) %>%
      #compute TMS effects for each subject * condition
      mutate(Accuracy_TMS_effect = Accuracy_score-Accuracy_score[TW == "ctrlTMS"]) %>%
      mutate(Error_rate_TMS_effect = Error_rate-Error_rate[TW == "ctrlTMS"]) %>%
      filter(TW != "ctrlTMS")

# Create summaries with % (* 100)
raw_accu_tms_summaries <- accu_tms_effects %>%
    group_by(Group, Site, Modality, TW) %>%
    dplyr::summarise(mean = mean(Accuracy_TMS_effect) * 100,
                     sem = (sd(Accuracy_TMS_effect)/sqrt(25)) * 100)

rm(accu_tms_effects, accu_data_all)

#smol clean-up
rm(blind_accuracy_data, sighted_accuracy_data,
   blind_rt_data, sighted_rt_data,
   blind_raw_data, sighted_raw_data, 
   tms_preproc, blind_percent_trimmed, 
   sighted_percent_trimmed)

```


ACCURACY: GLMMs (BINOMIAL):

GROUP x SITE x TW x MODALITY: MODEL

```{r ACCURACY, include = FALSE}

#binomial glmer with binary accuracy: NULL MODEL (intercept only)
accu.glm.null <- glmer(Accuracy_01 ~ (1|Subject), 
                       data = raw_data_all, 
                       family = "binomial",
                       nAGQ = 0, 
                       control = glmerControl(optimizer = "nloptwrap"))


#binomial glmer with binary accuracy
accu.glm.full <- glmer(Accuracy_01 ~ Group * Modality * Site * TW * Lex 
                       + (1|Letters) + (1|Subject),
                  data = raw_data_all, 
                  family = "binomial", 
                  nAGQ = 0, 
                  control = glmerControl(optimizer = "nloptwrap"))

#Compare to null model
anova(accu.glm.null, accu.glm.full)

#ANOVA WALD Z on the main model
accu.glm.full.anova <- car::Anova(accu.glm.full, type = 3)

## Model summary
summary(accu.glm.full)


# ##Plot inspections (Model diagnostics)
# plot(accu.glm)
# # normality of residuals
#  qqnorm(residuals(accu.glm))
#  qqline(residuals(accu.glm))
# # normality of random effect
#  qqnorm(ranef(accu.glm)$Subject[,1])
#  qqline(ranef(accu.glm)$Subject[,1])
# # random effects distributions
# library(lattice)
# dotplot(ranef(accu.glm,condVar=TRUE))

# to look at global effects of factors (anova-like)
# satterthwaite degrees of freedom approximation methods


# R SQUARED FOR THE MODEL - DOESN'T MAKE MUCH SENSE WITH THIS VARIANCE?

#library("piecewiseSEM")
#rsquared(accu.glm.full, method = NULL)


```

GROUP x SITE x TW x MODALITY: EMMEANS EXTRACTION

```{r}
# Get the Estimated Marginal Means for significant main effects and interactions:



# INTERACTIONS
accu.glm.full.EMMs.group.mod.TW.inter <- emmeans(accu.glm.full, 
                                                 list(pairwise ~Group*Modality*TW), 
                                                 adjust = "none")

accu.glm.full.EMMs.group.mod.TW.inter.list <-list(
    "emmeans" = data.frame(summary(accu.glm.full.EMMs.group.mod.TW.inter[["emmeans of Group, Modality, TW"]])),
    "comp" = data.frame(summary(accu.glm.full.EMMs.group.mod.TW.inter[["pairwise differences of Group, Modality, TW"]])))

accu.glm.full.EMMs.group.mod.site.inter <- emmeans(accu.glm.full, 
                                                 list(pairwise ~Group*Modality*Site), 
                                                 adjust = "none")

accu.glm.full.EMMs.group.mod.site.inter.list <-list(
    "emmeans" = data.frame(summary(accu.glm.full.EMMs.group.mod.site.inter[["emmeans of Group, Modality, Site"]])),
    "comp" = data.frame(summary(accu.glm.full.EMMs.group.mod.site.inter[["pairwise differences of Group, Modality, Site"]])))

##Exploratory: 4-way-interaction
accu.glm.full.EMMs.4way.inter <- emmeans(accu.glm.full, 
                                                 list(pairwise ~Group*Modality*Site*TW), 
                                                 adjust = "none")

accu.glm.full.EMMs.4way.inter.list <-list(
    "emmeans" = data.frame(summary(accu.glm.full.EMMs.4way.inter[["emmeans of Group, Modality, Site, TW"]])),
    "comp" = data.frame(summary(accu.glm.full.EMMs.4way.inter[["pairwise differences of Group, Modality, Site, TW"]])))


## AGGREGATE EVERYTHING INTO A LIST & CLEAN UP

accu.glm.full.SIG_EMMs <- list(
                          "Group:Modality:TW" = 
                              accu.glm.full.EMMs.group.mod.TW.inter.list, 
                          "Group:Modality:Site" = 
                              accu.glm.full.EMMs.group.mod.site.inter.list, 
                          "Exploratory 4-way Interaction" = 
                              accu.glm.full.EMMs.4way.inter.list)

rm(list = ls(pattern = "^accu.glm.full.EMMs_*"))
```

Accuracy: group-specific SITE x TW x MODALITY MODELs

```{r}

## ---------- BLIND: SPECIFY THE MODEL & DIAGNOSTICS ----------

accu.glm.blind <- raw_data_all %>% 
    filter(Group == "Blind") %>% 
    glmer(Accuracy_01 ~ Modality * Site * TW * Lex + (1|Subject) + (1|Letters),
                  data = ., 
                  family = "binomial", 
                  nAGQ = 0, 
                  control = glmerControl(optimizer = "nloptwrap"))

accu.glm.blind.anova <- car::Anova(accu.glm.blind, type = 3)
summary(accu.glm.blind)


## ---------- SIGHTED: SPECIFY THE MODEL & DIAGNOSTICS ----------


accu.glm.sighted <- raw_data_all %>% 
    filter(Group == "Sighted") %>% 
    glmer(Accuracy_01 ~Modality * Site * TW * Lex + (1|Subject) + (1|Letters),
                  data = ., 
                  family = "binomial", 
                  nAGQ = 0, 
                  control = glmerControl(optimizer = "nloptwrap"))

accu.glm.sighted.anova <- car::Anova(accu.glm.sighted, type = 3)
summary(accu.glm.sighted)

```

Accuracy: group-and-modality specific models (NOT JUSTIFIED BY INTERACTION ANALYSES)

```{r}
accu.glm.blind.read <-    raw_data_all %>% 
    filter(Group == "Blind" & Modality == "read") %>% 
    glmer(Accuracy_01 ~ Site * TW * Lex + (1|Subject) + (1|Letters),
                  data = ., 
                  family = "binomial", 
                  nAGQ = 0, 
                  control = glmerControl(optimizer = "nloptwrap"))

accu.glm.blind.speech <-    raw_data_all %>% 
    filter(Group == "Blind" & Modality == "speech") %>% 
    glmer(Accuracy_01 ~ Site * TW * Lex + (1|Subject) + (1|Letters),
                  data = ., 
                  family = "binomial", 
                  nAGQ = 0, 
                  control = glmerControl(optimizer = "nloptwrap"))

accu.glm.sighted.read <-    raw_data_all %>% 
    filter(Group == "Sighted" & Modality == "read") %>% 
    glmer(Accuracy_01 ~ Site * TW * Lex + (1|Subject) + (1|Letters),
                  data = ., 
                  family = "binomial", 
                  nAGQ = 0, 
                  control = glmerControl(optimizer = "nloptwrap"))


accu.glm.sighted.speech <-    raw_data_all %>% 
    filter(Group == "Sighted" & Modality == "speech") %>% 
    glmer(Accuracy_01 ~ Site * TW * Lex + (1|Subject) + (1|Letters),
                  data = ., 
                  family = "binomial", 
                  nAGQ = 0, 
                  control = glmerControl(optimizer = "nloptwrap"))

```

ANOVAS (Group-modality-specific GLMs)

```{r}
car::Anova(accu.glm.blind.read, type = 3) # NOTHING SIGNIFICANT
car::Anova(accu.glm.blind.speech, type = 3) #TRENING SITE & TW
car::Anova(accu.glm.sighted.read, type = 3) #MAIN EFFECT OF LEXICALITY
car::Anova(accu.glm.sighted.speech, type = 3) # NOTHING SIGNIFICANT
```

Accuracy: EMMEANS EXTRACTION

```{r}
accu.glm.blind.read.emmeans <-  data.frame(summary(emmeans(accu.glm.blind.read,
                                                  pairwise ~Site*TW,
                                                  by = "Site",
                                                  adjust = "none")$contrast))

accu.glm.blind.speech.emmeans <-  data.frame(summary(emmeans(accu.glm.blind.speech,
                                                  pairwise ~Site*TW,
                                                  by = "Site",
                                                  adjust = "none")$contrast))

accu.glm.sighted.read.emmeans <-  data.frame(summary(emmeans(accu.glm.sighted.read,
                                                  pairwise ~Site*TW,
                                                  by = "Site",
                                                  adjust = "none")$contrast))

accu.glm.sighted.speech.emmeans <-  data.frame(summary(emmeans(accu.glm.sighted.speech,
                                                  pairwise ~Site*TW,
                                                  by = "Site",
                                                  adjust = "none")$contrast))
```

JOIN THE EMMEANS INTO A SINGLE DF

```{r}
#NOTHING IS SIGNIFICANT, ONLY NEEDED FOR BREWITY OF REPORTING 
accu_time_contrasts_df <- 
        rbind(accu.glm.blind.read.emmeans, accu.glm.blind.speech.emmeans,
              accu.glm.sighted.read.emmeans, accu.glm.sighted.speech.emmeans) %>% 
        mutate(Group = rep(c("Blind", "Sighted"), each = 24)) %>%
        mutate(Modality = rep(c("read", "speech"), each = 12, times = 2)) %>% 
        mutate(estimate_inv = estimate * (-1)) %>% 
        mutate(p_adj24 = p.value*24) %>% 
        mutate(p_signif = 
                   ifelse(p_adj24 < 0.001, "***", 
                      ifelse(p_adj24 < 0.01, "**", 
                             ifelse(p_adj24 < 0.05, "*",
                                    ifelse(p_adj24<0.1, "t", "ns"))))) %>% 
        dplyr::select(Group, Modality, Site, contrast, estimate_inv, everything())
```

Accuracy: LEXICALITY EFFECTS (MAIN EFFECT OF LEX)

```{r}
me_lex_bl.rd <- data.frame(summary(emmeans(accu.glm.blind.read, ~Lex)))
me_lex_bl.sp <- data.frame(summary(emmeans(accu.glm.blind.speech, ~Lex)))
me_lex_si.rd <- data.frame(summary(emmeans(accu.glm.sighted.read, ~Lex)))
me_lex_si.sp <- data.frame(summary(emmeans(accu.glm.sighted.speech, ~Lex)))


#Gather main effects (emmeans) to plot beside temporal patters
df.accu.glm.lex_me <- rbind(me_lex_bl.rd, me_lex_bl.sp, 
                           me_lex_si.rd, me_lex_si.sp) %>% 
    mutate(Group = rep(c("Blind", "Sighted"), each = 4)) %>% 
    mutate(Modality = rep(c("read", "speech"), each = 2, times = 2)) %>% 
    dplyr::select(Group, Modality, everything())


#COMPARE LEXICALITY (MAIN EFFECT)

comp_accu_lex_bl.rd <- data.frame(summary(emmeans(accu.glm.blind.read,
                                             pairwise ~Lex)$contrast))
comp_accu_lex_bl.sp <- data.frame(summary(emmeans(accu.glm.blind.speech,
                                             pairwise ~Lex)$contrast))
comp_accu_lex_si.rd <- data.frame(summary(emmeans(accu.glm.sighted.read,
                                             pairwise ~Lex)$contrast))
comp_accu_lex_si.sp <- data.frame(summary(emmeans(accu.glm.sighted.speech,
                                             pairwise ~Lex)$contrast))


# DF with comparisons of main effects - were they significant in the models? 
lex_accu_me_comp_df <- rbind(comp_accu_lex_bl.rd, comp_accu_lex_bl.sp, 
                           comp_accu_lex_si.rd, comp_accu_lex_si.sp) %>% 
    mutate(Group = rep(c("Blind", "Sighted"), each = 2)) %>% 
    mutate(Modality = rep(c("read", "speech"), times = 2)) %>% 
    dplyr::select(Group, Modality, everything())


rm(list = ls(pattern = "^me_lex*"))
rm(list = ls(pattern = "^comp_accu_lex*"))
```

Accuracy: LEXICALITY EFFECTS (ACROSS TIME)

```{r}

lex.accu.blind.read.emmeans <-  data.frame(summary(emmeans(accu.glm.blind.read,
                                                  pairwise ~Lex*Site*TW,
                                                  by = c("Site", "Lex"),
                                                  adjust = "none")$contrast))

lex.accu.blind.speech.emmeans <-  data.frame(summary(emmeans(accu.glm.blind.speech,
                                                  pairwise ~Lex*Site*TW,
                                                  by = c("Site", "Lex"),
                                                  adjust = "none")$contrast))

lex.accu.sighted.read.emmeans <-  data.frame(summary(emmeans(accu.glm.sighted.read,
                                                  pairwise ~Lex*Site*TW,
                                                  by = c("Site", "Lex"),
                                                  adjust = "none")$contrast))

lex.accu.sighted.speech.emmeans <-  data.frame(summary(emmeans(accu.glm.sighted.speech,
                                                  pairwise ~Lex*Site*TW,
                                                  by = c("Site", "Lex"),
                                                  adjust = "none")$contrast))

#JOIN INTO LEX TIME DF 
df.lex_accu_time_contrasts <- rbind(lex.accu.blind.read.emmeans, 
                                    lex.accu.blind.speech.emmeans,
                                    lex.accu.sighted.read.emmeans,
                                    lex.accu.sighted.speech.emmeans) %>% 
        mutate(Group = rep(c("Blind", "Sighted"), each = 48)) %>%
        mutate(Modality = rep(c("read", "speech"), each = 24, times = 2)) %>% 
        mutate(estimate_inv = estimate * (-1)) %>% 
        mutate(p_adj48 = p.value*48) %>% 
        mutate(p_signif = 
                   ifelse(p_adj48 < 0.001, "***", 
                      ifelse(p_adj48 < 0.01, "**", 
                             ifelse(p_adj48 < 0.05, "*",
                                    ifelse(p_adj48<0.1, "t", "ns"))))) %>% 
        dplyr::select(Group, Modality, Site, contrast, estimate_inv, everything())
    
```

LEXICALITY: words vs pseudowords [TMS effects magnitude]
Endproduct: accu_lex_word_pseudo_comp_df
```{r}
# COMPARE THE MAGNITUDE OF TMS EFFECTS (TW - CTRL TW between words and pseudowords in each TW/SITE, eg. EVC EARLY TMS - CTRL TMS: WORDS - PSEUDO)

# Try to extract pairs of TW - CONTROL TW [words vs pseudo]


# Extract only relevant rows
accu_word_pseudo_bl.rd <- avg_comparisons(accu.glm.blind.read,
    variables = "TW",
    by = c("Lex", "Site"),
    hypothesis = "pairwise")[c(c(1, 39, 61, 22, 52, 66)), ]

accu_word_pseudo_bl.sp <- avg_comparisons(accu.glm.blind.speech,
    variables = "TW",
    by = c("Lex", "Site"),
    hypothesis = "pairwise")[c(c(1, 39, 61, 22, 52, 66)), ]

accu_word_pseudo_si.rd <- avg_comparisons(accu.glm.sighted.read,
    variables = "TW",
    by = c("Lex", "Site"),
    hypothesis = "pairwise")[c(c(1, 39, 61, 22, 52, 66)), ]

accu_word_pseudo_si.sp <- avg_comparisons(accu.glm.sighted.speech,
    variables = "TW",
    by = c("Lex", "Site"),
    hypothesis = "pairwise")[c(c(1, 39, 61, 22, 52, 66)), ]

# JOIN THE DFs 
df.accu.lex_word_pseudo_comp <- rbind(accu_word_pseudo_bl.rd, accu_word_pseudo_bl.sp, 
                            accu_word_pseudo_si.rd, accu_word_pseudo_si.sp) %>% 
    mutate(Group = rep(c("Blind", "Sighted"), each = 12)) %>% 
    mutate(Modality = rep(c("read", "speech"), each = 6, times = 2)) %>% 
    mutate(Site = rep(c("EVC", "VWFA"), each = 3, times = 4)) %>% 
    mutate(TW = rep(c("earlyTMS", "midTMS", "lateTMS"), times = 8)) %>% 
    mutate(p_adj48 = p.value*48) %>% 
    mutate(p_signif = 
                   ifelse(p_adj48 < 0.001, "***", 
                      ifelse(p_adj48 < 0.01, "**", 
                             ifelse(p_adj48 < 0.05, "*",
                                    ifelse(p_adj48<0.1, "t", "ns"))))) %>% 
    dplyr::select(Group, Modality, Site, TW, everything())

rm(list = ls(pattern = "^accu_word_pseudo*"))

```


ACCU PLOTS (MAIN)

```{r}

#Prepare DF for plotting 

df.accu.glm.tms.effects <- accu_time_contrasts_df %>% 
    filter(grepl("ctrlTMS", contrast)) %>% 
    mutate(TW = gsub("ctrlTMS - ", "", contrast)) %>% 
    mutate(TW = factor(TW, levels = c("earlyTMS", "midTMS", "lateTMS"))) %>% 
    dplyr::select(Group, Site, Modality, TW, everything()) %>% 
    dplyr::select(-c(estimate, contrast)) %>% 
    # copy plotted variables with names compatibile with plotting function (lazyness)
    mutate(estimate = estimate_inv) 
    
```

LEXICALITY PLOT DF

```{r}

#Prepare DF with TMS effects across lexicalities

df.accu.glm.lex_time_tms_effects <- df.lex_accu_time_contrasts %>% 
    filter(grepl("ctrlTMS", contrast)) %>% 
    mutate(TW = gsub("ctrlTMS - ", "", contrast)) %>% 
    mutate(TW = factor(TW, levels = c("earlyTMS", "midTMS", "lateTMS"))) %>% 
    mutate(Lex = factor(Lex, levels = c("word", "pseudo"))) %>% 
    dplyr::select(Group, Site, Modality, TW, Lex, everything()) %>% 
    dplyr::select(-c(estimate, contrast)) %>% 
    # copy plotted variables with names compatibile with plotting function (lazyness)
    mutate(estimate = estimate_inv)


```

---------- SAVE DATA FOR PLOTS ----------

GLM plots require following data frames: 
- df.accu.glm.tms.effects
- df.accu.glm.lex_time_tms_effects
- df.accu.glm.lex_me

```{r}

save(df.accu.glm.tms.effects, df.accu.glm.lex_time_tms_effects, df.accu.glm.lex_me, 
     file = paste(dir, 'data', 'TMS','GLM_ACCU_plot_data.RData', sep = '/'))
```
