---
title: "fMRI_chronoTMS_Blind_Sighted_TMS_RT"
author: "Jacek Matuszewski"
date: '2022-08-16'
output: html_document
---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, echo=, message=FALSE, warning=FALSE}
#library(plotly)
library(tidyverse)
library(lme4)
library(lmerTest)
library(jtools)
library(tidyverse)
library(stringr)
library(nlme)
library(marginaleffects)
library(emmeans)
library(RColorBrewer)
```

WORKFLOW FOR THIS SCRIPT:

1.  Load the libraries
2.  Load the raw (preprocessed) data and select only CORRECT responses for RT analyses
3.  Exclude the tired subject (Sighted_11)
4.  Specify 4 types of linear models:
    1.  GROUP-SPECIFIC model including both sensory modalities to test for TW x Site x Modality interaction, no follow-up EMMEANS analyses

    2.  Two GROUP-MODALITY-SPECIFIC models including only one sensory modality to test for TW x Site interaction.

    3.  BIG GROUP-SITE-TW-MODALITY NLME model to test for a 4-way interaction [only to show lack of it], no follow-up EMMEANS analyses? [varident group\*modality]
5.  RUN THE EMMEANS / AVG PREDICTED analyses to test for:
    1.  TMS effects (comparisons to ctrl time window) [emmeans]

    2.  Temporal specificity (comparisons across other time windows within site/modality) [emmeans]

    3.  Differences across SITES - comparisons of the magnitude of TMS effects across sites [exploratory, marginal effects pck]
6.  RUN THE EMMEANS / AVG PREDICTED analyses to test for LEXICALITY EFFECTS (main effect of lexicality vs interactions?)
    1.  Either plot one big contrast across groups for each modality as an intro OR

    2.  Use summarized individual predicted values (by subject) for "CPP Plots"



```{r Load preprocessed data, echo=}
#Requires running TMS_MNI_and_preproc.Rmd first
#rm(list=ls())
#load("~/Documents/Preludium_JM_roboczo/Data/TMS_preprocessed_data.RData")

dir <- '/Users/jacekmatuszewski/Documents/GitHub/fMRI_chronoTMS_Blind_Sighted'

load(paste(dir, 'data', 'TMS', 'TMS_preprocessed_data.RData', sep = '/'))

raw_data_all <- rbind(blind_raw_data, sighted_raw_data)
raw_data_correct <- raw_data_all %>% 
    filter(Accuracy == "hit" & Subject != "Sighted_11")
 
#Recode to factors for modelling
raw_data_correct$Site <- as.factor(raw_data_correct$Site)
raw_data_correct$TW <- as.factor(raw_data_correct$TW)
raw_data_correct$Lex <- as.factor(raw_data_correct$Lex)
raw_data_correct$Group <- as.factor(raw_data_correct$Group)
raw_data_correct$Modality <- as.factor(raw_data_correct$Modality)
raw_data_correct$Letters <- as.factor(raw_data_correct$Letters)

#smol clean-up
rm(blind_accuracy_data, sighted_accuracy_data,
   blind_rt_data, sighted_rt_data,
   blind_raw_data, sighted_raw_data, raw_data_all,
   blind_percent_trimmed, sighted_percent_trimmed, 
   tms_preproc)

```

---------- MAIN ANALYSES ----------


LMER: BLIND TW x MODALITY x SITE INTERACTION

```{r}

## RT GLM FOR BLIND
#null model
rt.glm.blind.null <- raw_data_correct %>% 
    filter(Group == "Blind") %>% 
    lmer(RT ~ (1|Subject),
                  data = .)

#full model
rt.glm.blind.lex <- raw_data_correct %>% 
    filter(Group == "Blind") %>% 
    lmer(RT ~ Modality * Site * TW * Lex + (1|Letters) + (1|Subject),
                  data = .)
#Anova: null vs full
anova(rt.glm.blind.null, rt.glm.blind.lex) #base, can only compare 2 models

#Anova: full model
anova(rt.glm.blind.lex, type = "III", ddf="Satterthwaite") #quick estimation
#anova(rt.glm.blind.lex, type = "III", ddf="Kenward-Roger") #long computation
#stats::anova(rt.glm.blind.lex)
#car::Anova(rt.glm.blind.lex, type = 3)

```

LMER: BLIND READING + EMMEANS

```{r}
## EMMEANS for BLIND make no sense, SEs equal in reading and speech, compute modality-specific models for proper EMMEANS


## RT GLM FOR BLIND: MODALITY-SPECIFIC
rt.glm.blind.lex.read <- raw_data_correct %>% 
    filter(Group == "Blind" & Modality == "read") %>% 
        #filter(Group == "Blind" & Modality == "read" & Subject!= "Blind_6") %>% 
    lmer(RT ~ Site * TW * Lex + (1|Letters) + (1|Subject),
                  data = .)



#anova(rt.glm.blind.lex.read, type = "III")


## EMMEANS: READING

#INTERACTIONS: contrasts between TIME WINDWOWS by Site (EVC, VWFA separately)
rt.glm.blind.read.emmeans <-  data.frame(summary(emmeans(rt.glm.blind.lex.read,
                                                  pairwise ~Site*TW,
                                                  by = "Site",
                                                 adjust = "none")$contrast))


```

LMER: BLIND SPEECH + EMMEANS

```{r}
## EMMEANS: SPEECH
rt.glm.blind.lex.speech <- raw_data_correct %>% 
    filter(Group == "Blind" & Modality == "speech") %>% 
    lmer(RT ~ Site * TW * Lex + (1|Letters) + (1|Subject),
                  data = .)

#anova(rt.glm.blind.lex.speech, type = "III")

## EMMEANS: SPEECH

#INTERACTIONS: contrasts between TIME WINDWOWS by Site (EVC, VWFA separately)
rt.glm.blind.speech.emmeans <-  data.frame(summary(emmeans(rt.glm.blind.lex.speech,
                                                  pairwise ~Site*TW,
                                                  by = "Site",
                                                 adjust = "none")$contrast))
```

LMER: SIGHTED TW x MODALITY x SITE INTERACTION

```{r}

## RT GLM FOR SIGHTED 

rt.glm.sighted.null <- raw_data_correct %>% 
    filter(Group == "Sighted") %>% 
    lmer(RT ~  (1|Subject),
                  data = .)


rt.glm.sighted.lex <- raw_data_correct %>% 
    filter(Group == "Sighted") %>% 
    lmer(RT ~ Modality * Site * TW * Lex + (1|Letters) + (1|Subject),
                  data = .)
#anova null vs full
anova(rt.glm.sighted.null, rt.glm.sighted.lex)

anova(rt.glm.sighted.lex, type = "III")
#car::Anova(rt.glm.blind.lex, type = 3)

```

LMER: SIGHTED READING + EMMEANS

```{r}
## RT GLM FOR SIGHTED: MODALITY-SPECIFIC
rt.glm.sighted.lex.read <- raw_data_correct %>% 
    #filter(Group == "Sighted" & Modality == "read") %>% 
    filter(Group == "Sighted" & Modality == "read" & Subject != "Sighted_11") %>% 
    lmer(RT ~ Site * TW * Lex + (1|Letters) + (1|Subject),
                  data = .)

anova(rt.glm.sighted.lex.read, type = "III")

## EMMEANS: READ

#INTERACTIONS: contrasts between TIME WINDWOWS by Site (EVC, VWFA separately)
rt.glm.sighted.read.emmeans <-  data.frame(summary(emmeans(rt.glm.sighted.lex.read,
                                                  pairwise ~Site*TW,
                                                  by = "Site",
                                                 adjust = "none")$contrast))
```

LMER: SIGHTED SPEECH + EMMEANS

```{r}
rt.glm.sighted.lex.speech <- raw_data_correct %>% 
    filter(Group == "Sighted" & Modality == "speech") %>% 
    lmer(RT ~ Site * TW * Lex + (1|Letters) + (1|Subject),
                  data = .)

anova(rt.glm.sighted.lex.speech, type = "III")

## EMMEANS: SPEECH

#INTERACTIONS: contrasts between TIME WINDWOWS by Site (EVC, VWFA separately)
rt.glm.sighted.speech.emmeans <-  data.frame(summary(emmeans(rt.glm.sighted.lex.speech,
                                                  pairwise ~Site*TW,
                                                  by = "Site",
                                                 adjust = "none")$contrast))

```

JOIN ALL TIME COMPS IN ONE DF + ADD BONFERRONI & METADATA

```{r}

## GATHER EMMEANS DATA + add info about modalities, groups and sig with bonf corrections within each group

df.rt.contrasts.time <- 
        rbind(rt.glm.blind.read.emmeans, rt.glm.blind.speech.emmeans,
              rt.glm.sighted.read.emmeans, rt.glm.sighted.speech.emmeans) %>% 
        mutate(Group = rep(c("Blind", "Sighted"), each = 24)) %>%
        mutate(Modality = rep(c("read", "speech"), each = 12, times = 2)) %>% 
        mutate(estimate_inv = estimate * (-1)) %>% 
        mutate(p_adj24 = p.value*24) %>%
        mutate(p_signif = 
                   ifelse(p_adj24 < 0.001, "***", 
                      ifelse(p_adj24 < 0.01, "**", 
                             ifelse(p_adj24 < 0.05, "*",
                                    ifelse(p_adj24<0.1, "t", "ns"))))) %>% 
        dplyr::select(Group, Modality, Site, contrast, estimate_inv, everything())

#rm(list = ls(pattern = "*.emmeans"))
```

LMER: BIG 4-WAY INTERACTION (with lexicality controlled, only check GROUP x SITE x TIME)

```{r}
## RT GLM FOR BIG 4-WAY INTERACTION
# rt.glm.full <- lmer(RT ~ Group * Modality * Site * TW + Lex + (1|Letters) + (1|Subject),
#                   data = raw_data_correct)


rt.lme.full <- raw_data_correct %>% 
     nlme::lme(RT ~ Group * Modality * Site * TW +Lex,
                     random = list(~ 1 | Subject,
                                   ~ 1 | Letters),
                    weights = varIdent(form = ~1|Group*Modality),
                     data= .)


#anova(rt.lme.full, type = "III")
car::Anova(rt.lme.full, type = "III")
```


DIFFERENCES BETWEEN SITES (in TMS effects to keep TMS side effects controlled)
Endproduct: rt_site_contrasts_df

```{r}
## differences in differences? eg. comparing (V1 early - ctrl) - (VWFA early - ctrl) to control side effects and baseline RT differences?
# ONLY INTERESTNIG IS ROW 1 - 2 (early TMS effect across sites) ROW 3-4 (mid) & late (5-6)
## NO MULTIPLE COMP CORRECTIONS ARE DONE HERE
site_contrasts_bl.rd <- comparisons(
    rt.glm.blind.lex.read,
    variables = "TW",
    newdata = datagrid(Site = c("EVC", "VWFA")),
    hypothesis = "pairwise")[c(1,10,15), ] 
    

site_contrasts_bl.sp <- comparisons(
    rt.glm.blind.lex.speech,
    variables = "TW",
    newdata = datagrid(Site = c("EVC", "VWFA")),
    hypothesis = "pairwise")[c(1,10,15), ] 

site_contrasts_si.rd <- comparisons(
    rt.glm.sighted.lex.read,
    variables = "TW",
    newdata = datagrid(Site = c("EVC", "VWFA")),
    hypothesis = "pairwise")[c(1,10,15), ]


site_contrasts_si.sp <- comparisons(
    rt.glm.sighted.lex.speech,
    variables = "TW",
    newdata = datagrid(Site = c("EVC", "VWFA")),
    hypothesis = "pairwise")[c(1,10,15), ] 

## JOIN DFs and add metadata + bonferroni corrections
df.rt.contrasts.site <- rbind(site_contrasts_bl.rd, site_contrasts_bl.sp, 
                           site_contrasts_si.rd, site_contrasts_si.sp) %>% 
    mutate(comp = recode(term, "Row 1 - Row 2" = "Eearly TMS effect EVC - VWFA",
                         "Row 3 - Row 4" = "Mid TMS effect EVC - VWFA", 
                         "Row 5 - Row 6" = "Late TMS effect EVC - VWFA")) %>% 
    mutate(Group = rep(c("Blind", "Sighted"), each = 6)) %>% 
    mutate(Modality = rep(c("read", "speech"), each = 3, times = 2)) %>% 
    mutate(p.adjust3 = p.value*3) %>% 
    mutate(p.adjust12 = p.value*12) %>% 
    dplyr::select(Group, Modality, everything())


#clean up 
rm(list = ls(pattern = "^site_contrasts_*"))
```

PREPARE TMS EFFECTS DF FOR PLOTS!
Endproduct:  df.rt.glm.tms.effects
```{r}
#Try to aggregate all groups, sites and modalities for TW - ctrl TW emmeans contrast! 


df.rt.glm.tms.effects <- data.frame()

    #BLIND READING
    bl.rd <- rt.glm.blind.read.emmeans[c(1,2,3,7,8,9), ] %>% 
        mutate(Group = "Blind") %>% 
        mutate(Modality = "read") %>% 
        mutate(TW = rep(c("earlyTMS", "midTMS", "lateTMS"),2)) %>% 
        mutate(Site = rep(c("EVC", "VWFA"), each = 3))
    
    #BLIND SPEECH
    bl.sp <- rt.glm.blind.speech.emmeans[c(1,2,3,7,8,9), ] %>% 
        mutate(Group = "Blind") %>% 
        mutate(Modality = "speech") %>% 
        mutate(TW = rep(c("earlyTMS", "midTMS", "lateTMS"),2)) %>% 
        mutate(Site = rep(c("EVC", "VWFA"), each = 3))
    
    #SIGHTED READ
    si.rd <- rt.glm.sighted.read.emmeans[c(1,2,3,7,8,9), ] %>% 
        mutate(Group = "Sighted") %>% 
        mutate(Modality = "read") %>% 
        mutate(TW = rep(c("earlyTMS", "midTMS", "lateTMS"),2)) %>% 
        mutate(Site = rep(c("EVC", "VWFA"), each = 3))
    
    #SIGHTED SPEECH
    si.sp <- rt.glm.sighted.speech.emmeans[c(1,2,3,7,8,9), ] %>% 
        mutate(Group = "Sighted") %>% 
        mutate(Modality = "speech") %>% 
        mutate(TW = rep(c("earlyTMS", "midTMS", "lateTMS"),2)) %>% 
        mutate(Site = rep(c("EVC", "VWFA"), each = 3))
    
    
    #Bind and flip the effects
    df.rt.glm.tms.effects <- rbind(bl.rd, bl.sp, si.rd, si.sp) %>% 
        mutate(estimate = estimate * (-1)) %>% 
        mutate(t.ratio = t.ratio * (-1)) %>% 
        mutate(p_adj24 = p.value*24) %>% 
        mutate(p_signif = 
                   ifelse(p_adj24 < 0.001, "***", 
                      ifelse(p_adj24 < 0.01, "**", 
                             ifelse(p_adj24 < 0.05, "*",
                                    ifelse(p_adj24<0.1, "t", "ns"))))) %>% 
        dplyr::select(Group, Modality, Site, TW, everything())
    
    
    rm(bl.rd, bl.sp, si.rd, si.sp)
```

GATHER COMPARISONS BETWEEN OTHER TIME WINDOWS (within each site, group and modality)
Endproduct: rt.glm.tms.other.TWs
```{r}
rt.glm.tms.other.TWs <- data.frame()

    #BLIND READING
    bl.rd <- rt.glm.blind.read.emmeans[c(4,5,6,10,11,12), ] %>% 
        mutate(Group = "Blind") %>% 
        mutate(Modality = "read") %>% 
        mutate(TW = rep(c("earlyTMS", "midTMS", "lateTMS"),2)) %>% 
        mutate(Site = rep(c("EVC", "VWFA"), each = 3))
    
    #BLIND SPEECH
    bl.sp <- rt.glm.blind.speech.emmeans[c(4,5,6,10, 11, 12), ] %>% 
        mutate(Group = "Blind") %>% 
        mutate(Modality = "speech") %>% 
        mutate(TW = rep(c("earlyTMS", "midTMS", "lateTMS"),2)) %>% 
        mutate(Site = rep(c("EVC", "VWFA"), each = 3))
    
    #SIGHTED READ
    si.rd <- rt.glm.sighted.read.emmeans[c(4,5,6,10, 11, 12), ] %>% 
        mutate(Group = "Sighted") %>% 
        mutate(Modality = "read") %>% 
        mutate(TW = rep(c("earlyTMS", "midTMS", "lateTMS"),2)) %>% 
        mutate(Site = rep(c("EVC", "VWFA"), each = 3))
    
    #SIGHTED SPEECH
    si.sp <- rt.glm.sighted.speech.emmeans[c(4,5,6,10, 11, 12), ] %>% 
        mutate(Group = "Sighted") %>% 
        mutate(Modality = "speech") %>% 
        mutate(TW = rep(c("earlyTMS", "midTMS", "lateTMS"),2)) %>% 
        mutate(Site = rep(c("EVC", "VWFA"), each = 3))
    
    
    #Bind and flip the effects
    rt.glm.tms.other.TWs <- rbind(bl.rd, bl.sp, si.rd, si.sp) %>% 
        mutate(estimate = estimate * (-1)) %>% 
        mutate(t.ratio = t.ratio * (-1)) %>% 
        dplyr::select(Group, Modality, Site, TW, everything())
    
    
    rm(bl.rd, bl.sp, si.rd, si.sp)
```

---------- LEXICALITY EFFECTS ----------

MAIN EFFECTS & TIME EFFECTS
Endproduct: 
rt_lex_me_comp_df
rt.glm.lex_time_tms_effects_df

```{r}
## ---------- MAIN EFFECT OF LEXICALITY: emmeans for plots ----------

## Get the EMMEANS FOR WORDS AND PSEUDOWORDS IN EACH GROUP x MODALITY
#Easy way to get EMMEANS from summaries ("main effect of lexicality") 
me_lex_bl.rd <- data.frame(summary(emmeans(rt.glm.blind.lex.read, ~Lex)))
me_lex_bl.sp <- data.frame(summary(emmeans(rt.glm.blind.lex.speech, ~Lex)))
me_lex_si.rd <- data.frame(summary(emmeans(rt.glm.sighted.lex.read, ~Lex)))
me_lex_si.sp <- data.frame(summary(emmeans(rt.glm.sighted.lex.speech, ~Lex)))


#Gather main effects (emmeans) to plot beside temporal patters
df.rt.glm.lex_me <- rbind(me_lex_bl.rd, me_lex_bl.sp, 
                           me_lex_si.rd, me_lex_si.sp) %>% 
    mutate(Group = rep(c("Blind", "Sighted"), each = 4)) %>% 
    mutate(Modality = rep(c("read", "speech"), each = 2, times = 2)) %>% 
    dplyr::select(Group, Modality, everything())


## GET COMPARISON STATS FOR LEXICALITIES
comp_lex_bl.rd <- data.frame(summary(emmeans(rt.glm.blind.lex.read,
                                             pairwise ~Lex)$contrast))
comp_lex_bl.sp <- data.frame(summary(emmeans(rt.glm.blind.lex.speech,
                                             pairwise ~Lex)$contrast))
comp_lex_si.rd <- data.frame(summary(emmeans(rt.glm.sighted.lex.read,
                                             pairwise ~Lex)$contrast))
comp_lex_si.sp <- data.frame(summary(emmeans(rt.glm.sighted.lex.speech,
                                             pairwise ~Lex)$contrast))


df.rt_lex_me_comp <- rbind(comp_lex_bl.rd, comp_lex_bl.sp, 
                           comp_lex_si.rd, comp_lex_si.sp) %>% 
    mutate(Group = rep(c("Blind", "Sighted"), each = 2)) %>% 
    mutate(Modality = rep(c("read", "speech"), times = 2)) %>% 
    dplyr::select(Group, Modality, everything())

## ---------- LEXICALITY OVER TIME: emmeans for plots ----------

#Get the temporal patters for qualitative assesment (contrasts to ctrl across groups and modalities for words and pseudowords separately)

##BLIND
#READ
time_lex_bl.rd <- 
    data.frame(summary(emmeans(rt.glm.blind.lex.read,
                               pairwise ~Site*TW*Lex,
                               by = c("Site", "Lex"),
                               adjust = "none")$contrast))

#SPEECH
time_lex_bl.sp <- 
    data.frame(summary(emmeans(rt.glm.blind.lex.speech,
                               pairwise ~Site*TW*Lex,
                               by = c("Site", "Lex"),
                               adjust = "none")$contrast))


## SIGHTED
# READ
time_lex_si.rd <- 
    data.frame(summary(emmeans(rt.glm.sighted.lex.read,
                               pairwise ~Site*TW*Lex,
                               by = c("Site", "Lex"),
                               adjust = "none")$contrast))

# SPEECH
time_lex_si.sp <- 
    data.frame(summary(emmeans(rt.glm.sighted.lex.speech,
                               pairwise ~Site*TW*Lex,
                               by = c("Site", "Lex"),
                               adjust = "none")$contrast))


# JOIN THE DF
df.lex_time_comp <- rbind(time_lex_bl.rd, time_lex_bl.sp, time_lex_si.rd, time_lex_si.sp) %>% 
    mutate(Group = rep(c("Blind", "Sighted"), each = 48)) %>% 
    mutate(Modality = rep(c("read", "speech"), each = 24, times = 2)) %>% 
    mutate(estimate_inv = estimate* (-1)) %>% 
    mutate(p_adj24 = p.value*24) %>% 
    mutate(p_signif24 = 
                   ifelse(p_adj24 < 0.001, "***", 
                      ifelse(p_adj24 < 0.01, "**", 
                             ifelse(p_adj24 < 0.05, "*",
                                    ifelse(p_adj24<0.1, "t", "ns"))))) %>% 
    mutate(p_adj48 = p.value*48) %>% 
    mutate(p_signif48 = 
                   ifelse(p_adj48 < 0.001, "***", 
                      ifelse(p_adj48 < 0.01, "**", 
                             ifelse(p_adj48 < 0.05, "*",
                                    ifelse(p_adj48<0.1, "t", "ns"))))) %>% 
    dplyr::select(Group, Modality, everything())

df.rt.glm.lex_time_tms_effects <- df.lex_time_comp %>% 
    dplyr::arrange(contrast) %>% 
    dplyr::slice(1:48) %>% 
    mutate(estimate = estimate_inv) %>%
    mutate(contrast = (gsub("ctrlTMS - ", "", contrast))) %>% 
    dplyr::select(-estimate_inv)


#clean up
rm(list = ls(pattern = "^time_lex*"))
rm(list = ls(pattern = "^me_lex*"))
rm(list = ls(pattern = "^comp_lex*"))
```

LEXICALITY: words vs pseudowords [TMS effects magnitude]
Endproduct: lex_word_pseudo_comp_df
```{r}
# COMPARE THE MAGNITUDE OF TMS EFFECTS (TW - CTRL TW between words and pseudowords in each TW/SITE, eg. EVC EARLY TMS - CTRL TMS: WORDS - PSEUDO)

# Try to extract pairs of TW - CONTROL TW [words vs pseudo]


# c <- avg_comparisons(rt.glm.blind.lex.read,
#     variables = "TW",
#     by = c("Site", "Lex"))

# Extract only relevant rows
word_pseudo_bl.rd <- avg_comparisons(rt.glm.blind.lex.read,
    variables = "TW",
    by = c("Lex", "Site"),
    hypothesis = "pairwise")[c(c(1, 39, 61, 22, 52, 66)), ]

word_pseudo_bl.sp <- avg_comparisons(rt.glm.blind.lex.speech,
    variables = "TW",
    by = c("Lex", "Site"),
    hypothesis = "pairwise")[c(c(1, 39, 61, 22, 52, 66)), ]

word_pseudo_si.rd <- avg_comparisons(rt.glm.sighted.lex.read,
    variables = "TW",
    by = c("Lex", "Site"),
    hypothesis = "pairwise")[c(c(1, 39, 61, 22, 52, 66)), ]

word_pseudo_si.sp <- avg_comparisons(rt.glm.sighted.lex.speech,
    variables = "TW",
    by = c("Lex", "Site"),
    hypothesis = "pairwise")[c(c(1, 39, 61, 22, 52, 66)), ]

# JOIN THE DFs 
df.lex_word_pseudo_comp <- rbind(word_pseudo_bl.rd, word_pseudo_bl.sp, 
                            word_pseudo_si.rd, word_pseudo_si.sp) %>% 
    mutate(Group = rep(c("Blind", "Sighted"), each = 12)) %>% 
    mutate(Modality = rep(c("read", "speech"), each = 6, times = 2)) %>% 
    mutate(Site = rep(c("EVC", "VWFA"), each = 3, times = 4)) %>% 
    mutate(TW = rep(c("earlyTMS", "midTMS", "lateTMS"), times = 8)) %>% 
    mutate(p_adj24 = p.value*24) %>% 
    mutate(p_signif = 
                   ifelse(p_adj24 < 0.001, "***", 
                      ifelse(p_adj24 < 0.01, "**", 
                             ifelse(p_adj24 < 0.05, "*",
                                    ifelse(p_adj24<0.1, "t", "ns"))))) %>% 
    dplyr::select(Group, Modality, Site, TW, everything())

rm(list = ls(pattern = "^word_pseudo*"))

```

LINEAR CONTRASTS WITH EMMEANS 
https://marginaleffects.com/articles/hypothesis.html#complex-contrast

Linear contrasts for reading and speech
```{r}
#em <- emmeans(mod, "carb")
#lc <- data.frame(custom_contrast = c(-2, 1, 1, 0, -1, 1))
#contrast(em, method = lc)

#Define linear increase contrast
lc <- data.frame(custom_contrast = c(-3,-1,1,3))

#Get emmeans from each GLM
emmeans.blind.read <- emmeans(rt.glm.blind.lex.read, ~Site*TW,  by = "Site")
emmeans.blind.speech <- emmeans(rt.glm.blind.lex.speech, ~Site*TW, by = "Site")
emmeans.sighted.read <- emmeans(rt.glm.sighted.lex.read, ~Site*TW,  by = "Site")
emmeans.sighted.speech <- emmeans(rt.glm.sighted.lex.speech, ~Site*TW, by = "Site")

#Test the linear contrasts
contrast(emmeans.blind.read, method = lc)
contrast(emmeans.blind.speech, method = lc)
contrast(emmeans.sighted.read, method = lc)
contrast(emmeans.sighted.speech, method = lc)
```

Linear contrasts for LEXICALITY
```{r}
#em <- emmeans(mod, "carb")
#lc <- data.frame(custom_contrast = c(-2, 1, 1, 0, -1, 1))
#contrast(em, method = lc)

#Define linear increase contrast
lc <- data.frame(custom_contrast = c(-3,-1,1,3))

#Get emmeans from each GLM
emmeans.blind.read.lex <- emmeans(rt.glm.blind.lex.read, ~Site*TW,  by = c("Site", "Lex"))
emmeans.blind.speech.lex <- emmeans(rt.glm.blind.lex.speech, ~Site*TW, by = c("Site", "Lex"))
emmeans.sighted.read.lex <- emmeans(rt.glm.sighted.lex.read, ~Site*TW, by = c("Site", "Lex"))
emmeans.sighted.speech.lex <- emmeans(rt.glm.sighted.lex.speech, ~Site*TW, by = c("Site", "Lex"))

#Test the linear contrasts
# MULTIPLY P VALUES x 4 for multiple comparisons! 
contrast(emmeans.blind.read.lex, method = lc)
contrast(emmeans.blind.speech.lex, method = lc)
contrast(emmeans.sighted.read.lex, method = lc)
contrast(emmeans.sighted.speech.lex, method = lc)
```


---------- SAVE DATA FOR PLOTS ----------

GLM plots require following data frames: 
- df.rt.glm.tms.effects
- df.rt.glm.lex_time_tms_effects
- df.rt.glm.lex_me

```{r}
#load("~/Documents/Preludium_JM_roboczo/Data/TMS_preprocessed_data_test.RData")

save(df.rt.glm.tms.effects, df.rt.glm.lex_time_tms_effects, df.rt.glm.lex_me, 
     file = paste(dir, 'data', 'TMS','GLM_RT_plot_data.RData', sep = '/'))
```

CLEAN-UP?
```{r}
rm(list = ls(pattern = "*.emmeans"))
```

